### 2024-10-08 short/sections/projects.tex
Create projects.tex

\begin{cvhonors}
\cvhonor
{Making Finance Sustainable? A Comparative Perspective on the Politics of Investment}
{NWO VIDI SWG Project VI.Vidi.211.226, Research Associate (Natascha van der Zwan, Principal Investigator), about USD\$1 000 000. Period: 2024-2026.} %% {\pounds} 800 000
{Dutch Research Agency}
{2024}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Validación de un estándar de referencia para medir toxicidad e incivilidad política en la esfera digital}
{Internal Project 2024 at the Faculty of Administration and Economics at the Universidad Diego Portales (UDP), Principal Investigator, about USD\$2 000. Period: 2024-2025.} %% {\pounds} 1 500
{UDP}
{2024}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Large Language Models (LLMs) to Identify Toxicity in the Digital Sphere during Protest Events in Latin America}
{OpenAI Academic Programme, Principal Investigator, about USD\$5 000. Period: 2024.}
{OpenAI}
{2024}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Unravelling the Rule of Law: A Machine Learning Approach}
{NWO XS Project 406.XS.01.013, Research Associate (Jaroslaw Kantorowicz, Principal Investigator), about USD\$60 000. Period: 2023-2024.} %% {\pounds} 45 000
{Dutch Research Agency}
{2023}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Patrones territoriales de gobierno electrónico y abierto en los municipios chilenos}
{Internal Project USA 2156 POC2022\_FAE2 at the Universidad de Santiago de Chile (USACH), Principal Investigator, about USD\$2 250. Period: 2022.} %% {\pounds} 1 700
{USACH}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Sistema político y visibilidad de actores en el debate público articulado por la prensa de élite: 1990-2018}
{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), Research Associate (Ximena Orchard, Principal Investigator), about USD\$4 000. Period: 2019.} %% {\pounds} 3 000
{UAH}
{2019}
\end{cvhonors}

>>>>

\begin{cvhonors}
\cvhonor
{Making Finance Sustainable? A Comparative Perspective on the Politics of Investment}
{NWO VIDI SWG Project VI.Vidi.211.226, {\bfseries PostDoc} (Natascha van der Zwan, PI), about USD\$1 000 000. Period: 2024-2026.} %% {\pounds} 800 000
{Dutch Research Agency}
{2024}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Validación de un estándar de referencia para medir toxicidad e incivilidad política en la esfera digital}
{Internal Project 2024 at the Faculty of Administration and Economics at the Universidad Diego Portales (UDP), {\bfseries PI}, about USD\$2 000. Period: 2024-2025.} %% {\pounds} 1 500
{UDP}
{2024}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Large Language Models (LLMs) to Identify Toxicity in the Digital Sphere during Protest Events in Latin America}
{OpenAI Academic Programme, {\bfseries PI}, about USD\$5 000. Period: 2024.}
{OpenAI}
{2024}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Unravelling the Rule of Law: A Machine Learning Approach}
{NWO XS Project 406.XS.01.013, {\bfseries PostDoc} (Jaroslaw Kantorowicz, PI), about USD\$60 000. Period: 2023-2024.} %% {\pounds} 45 000
{Dutch Research Agency}
{2023}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Patrones territoriales de gobierno electrónico y abierto en los municipios chilenos}
{Internal Project USA 2156 POC2022\_FAE2 at the Universidad de Santiago de Chile (USACH), {\bfseries PI}, about USD\$2 250. Period: 2022.} %% {\pounds} 1 700
{USACH}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Sistema político y visibilidad de actores en el debate público articulado por la prensa de élite: 1990-2018}
{XVI Internal Competition for the Promotion of Research 2019 at the Universidad Alberto Hurtado (UAH), {\bfseries Research Associate} (Ximena Orchard, PI), about USD\$4 000. Period: 2019.} %% {\pounds} 3 000
{UAH}
{2019}
\end{cvhonors}
